### 2017-09-28 TF-vldb2018/sec-intro.tex

There has been a host of work on team formation by minimizing the communication cost of team members, based on the diameter, density, minimum spanning tree, Steiner tree, and sum of pairwise member distances among others \cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12,LiTongCao15}, which are essentially  a specialized class of keyword search on graphs~\cite{Aggarwal10}. Similar to~\cite{Kargar11}, we are to find top-$k$ teams. However, \cite{Kargar11} adopted Lawler's procedure \cite{Lawler1972}, and is inappropriate for large graphs. We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same lines as~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}. 
\revise{Except for simply minimizing the communication cost among team members, 
\cite{HuangLv16,Kargar11} consider minimizing the cost among team members and team leaders.}
Different from these work, we introduce {\em structural constraints}, in terms of graph pattern matching~\cite{FanLMTWW10,MaCFHW14}, into team formation, while retaining the capacity bounds on specific team members like~\cite{realTeamForm13,GajewarS12}.

>>>>

There has been a host of work on team formation by minimizing the communication cost of team members, based on the diameter, density, minimum spanning tree, Steiner tree, and sum of pairwise member distances among others \cite{Lappas09,Kargar11,ArisLuca12,GajewarS12,realTeamForm13,SamikKVM12,LiTongCao15}, which are essentially  a specialized class of keyword search on graphs~\cite{Aggarwal10}. Similar to~\cite{Kargar11}, we are to find top-$k$ teams. However, \cite{Kargar11} adopted Lawler's procedure \cite{Lawler1972}, and is inappropriate for large graphs. We also adopt {\em density}  as the communication cost, which shows a better performance~\cite{GajewarS12}, and further require that all team members are {\em close to each other} (located in the same balls), along the same line with~\cite{Lappas09,Kargar11,ArisLuca12,SamikKVM12}. 
\revise{Except for simply minimizing the communication cost among team members, 
\cite{HuangLv16,Kargar11} consider minimizing the cost among team members and team leaders.}
Different from these work, we introduce {\em structural constraints}, in terms of graph pattern matching~\cite{FanLMTWW10,MaCFHW14}, into team formation, while retaining the capacity bounds on specific team members like~\cite{realTeamForm13,GajewarS12}.
